The problem and promise of scale in multilayer networks

### 2020-02-02 paper/manuscript.Rmd
reorg social, spatial, temp in case study

### Caribou socioecology
Here, we use caribou as a case study to develop scale-dependent multilayer
networks based on temporal (seasonal), spatial (habitat type), and social
(visual and auditory perception). Caribou are gregarious ungulates with
fission-fusion dynamics (Lesmerises et al. 2018) that display temporal (Peignier
et al. 2019) and spatial (Webber et al. unpublished data) variation in social
networks. In winter, caribou dig holes in the snow, termed craters to access
forage (Bergerud 1974). As a result, caribou tend to occupy and re-use craters
once they are established and there is considerably less access to forage than
when the landscape is snow-free. Importantly, craters exist on the landscape at
multiple scales: the crater scale (a single crater), the feeding area scale
(multiple craters in close proximity), and the winter range scale (all craters
within an individual’s range) (Mayor et al. 2009). The distribution of forage
for caribou is therefore seasonally heterogeneous, with greater access in
snow-free seasons compared to winter as well as spatially heterogeneous in
winter because the distribution of craters on the landscape varies meaning that
access to vegetation in winter is highly variable for caribou. We therefore
partitioned data into two discrete seasons: <!-- TODO update these --> *summer
(3 August - 17 October) and winter (1 January – 16 March)* based on caribou
socioecology (Peignier et al. 2019).

>>>>

### Caribou socioecology
Here, we use caribou as a case study to develop scale-dependent multilayer
networks based on social (visual and auditory perception), spatial (habitat
type), and temporal (seasonal). Caribou are gregarious ungulates with
fission-fusion dynamics (Lesmerises et al. 2018) that display temporal [@Peignier_2019] and spatial (Webber et al. unpublished data) variation in social
networks. In winter, caribou dig holes in the snow, termed craters, to access
forage (Bergerud 1974). As a result, caribou tend to occupy and re-use craters
once they are established and there is considerably less access to forage than
when the landscape is snow-free. Importantly, craters exist on the landscape at
multiple scales: the crater scale (a single crater), the feeding area scale
(multiple craters in close proximity), and the winter range scale (all craters
within an individual’s range) (Mayor et al. 2009). The distribution of forage
for caribou is therefore seasonally heterogeneous, with greater access in
snow-free seasons compared to winter as well as spatially heterogeneous in
winter because the distribution of craters on the landscape varies meaning that
access to vegetation in winter is highly variable for caribou. We therefore
partitioned data into two discrete seasons: <!-- TODO update these --> *summer
(3 August - 17 October) and winter (1 January – 16 March)* based on caribou
socioecology (Peignier et al. 2019).
